Learning Features and Abstract Actions for Computing Generalized Plans

### 2018-11-10 doc/camera-ready/paper.tex
Fix some bib changes

@@

% Once again, although this set of abstract actions  is not complete,
% it is sufficient for generating a general plan.
The abstraction $Q_F$ with $I_F = \{ B>0, \neg X, G>0, C=0\}$ and $G_F = \{ B=0, C=0 \}$ is
translated into the FOND problem $Q^+_F$, which is solved by the
planner in 171.92 seconds. The resulting policy provably solves $\Q_{gripper}$,
meaning that it works for any  number of grippers and balls.
\Omit{ %% Add if space
The policy picks the balls in the source room, one by one, 
until the grippers are full or there are no more balls.
It then moves to the target room, with one of the two move actions above, 
according to whether the grippers are fully loaded or not,
and then drops the balls one by one, until the grippers
are all empty.  It then moves back to the other room if there   are still  balls
to be moved,  repeating the  process.
}

@@

\subsubsection{Acknowledgments.}
H. Geffner is partially funded by grant TIN-2015-67959-P, MINECO, Spain.
G. Franc\`{e}s is funded by the SSX project, European Research Council.

\bibliographystyle{aaai}
\bibliography{control}

\end{document}

>>>>

\providecommand{\noopsort}[1]{}

@@

% Once again, although this set of abstract actions  is not complete,
% it is sufficient for generating a general plan.
The abstraction $Q_F$ with $I_F\!=\!\{ B\!>\!0, \neg X, G\!>\!0, C\!=\!0\}$ and $G_F\!=\!\{ B\!=\!0, C\!=\!0 \}$ is
translated into the FOND problem $Q^+_F$, which is solved by the
planner in 171.92 seconds. The resulting policy provably solves $\Q_{gripper}$,
meaning that it works for any  number of grippers and balls.
\Omit{ %% Add if space
The policy picks the balls in the source room, one by one, 
until the grippers are full or there are no more balls.
It then moves to the target room, with one of the two move actions above, 
according to whether the grippers are fully loaded or not,
and then drops the balls one by one, until the grippers
are all empty.  It then moves back to the other room if there   are still  balls
to be moved,  repeating the  process.
}

@@

\subsubsection{Acknowledgments.}
H. Geffner is partially funded by grant TIN-2015-67959-P, MINECO, Spain;
G. Franc\`{e}s is funded by the SSX project, European Research Council.

\bibliographystyle{aaai}
\bibliography{control}
\end{document}
